Evaluating isolation and contact tracing for control of influenza outbreaks with pandemic potential: a modelling study

### 2025-06-19 inst/paper/main.tex
Update main.tex
Add conclusion

\item Mention strengths: interpretability, focus on average impact, speed

@@

\item This paper has focused on forward contact tracing. Backward contact tracing, whereby infected individuals are asked who they have been in contact with prior to being infected to identify the source of infection and potentially forward trace from the source, is applicable to infectious with long infectious periods (e.g. HIV), but is not effective for more ephemeral infections with faster transmission, as is the case for influenza.
\item Contact tracing and isolation is a targeted approach analogous to ring vaccination. It looks to prevent onward transmission by, either isolating or quarantining contacts in the case of contact tracing, or vaccinating contacts in the case of ring vaccination \citep{kucharskiEffectivenessRingVaccination2016, whittakerQuantifyingImpactBroadly2024}. Ring vaccination for an influenza outbreak would not be effective due to the generation time, proportion of presymptomatic and asymptomatic, and likelihood of geographically widespread (i.e. non-localised) transmission.

>>>>

\item Mention strengths: interpretability, focus on average impact, speed. R captures distribution of secondary transmission in population in concise way.

@@

\item Focus more on punchline, i.e. should not assume contact tracing useless for flu given current tools, and intermediate emergence characteristics (i.e. slower spread) may offer larger opportunity for window of control.
%\item This paper has focused on forward contact tracing. Backward contact tracing, whereby infected individuals are asked who they have been in contact with prior to being infected to identify the source of infection and potentially forward trace from the source, is applicable to infectious with long infectious periods (e.g. HIV), but is not effective for more ephemeral infections with faster transmission, as is the case for influenza.
%\item Contact tracing and isolation is a targeted approach analogous to ring vaccination. It looks to prevent onward transmission by, either isolating or quarantining contacts in the case of contact tracing, or vaccinating contacts in the case of ring vaccination \citep{kucharskiEffectivenessRingVaccination2016, whittakerQuantifyingImpactBroadly2024}. Ring vaccination for an influenza outbreak would not be effective due to the generation time, proportion of presymptomatic and asymptomatic, and likelihood of geographically widespread (i.e. non-localised) transmission.
